---
title: "Mission: Iconic Reef"
author: "[Jeremiah Blondeau](https://github.com/jeremiaheb) + Rob Harper"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "jeremiah.blondeau@noaa.gov"
github: "jeremiaheb/MissionIconicReef"
logo: "noaa_logo.png"
output:
  pdf_document:
    toc: true
    number_sections: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Needed Libraries
library(rvc)
library(tidyverse)
library(DT)

# Source Plotting Functions
source('code/labeler.R', local = knitr::knit_global())
source('code/QL_binned_LengthFreq.R', local = knitr::knit_global())
source('code/theme_publication.R', local = knitr::knit_global())
source('code/WrapperFunctions.R', local = knitr::knit_global())
source('code/MIR_Plot_functions.R', local = knitr::knit_global())

# Read in MIR data set
MIR_data <- readRDS("../data/MIR_Dataset.rds")
```

## The Data

The RVC, stationary-point-count method is modified from Bohnsack and Bannerot (1986) and is conducted on shallow (<100ft), hardbottom coral reef habitats. Field surveys use a one-stage design to sample 50 m x 50 m grid cells selected using a stratified-random sampling allocation. This data set represents sample locations in the Florida Keys. Only those strata types found within the MIR areas were considered (table 1).

```{r echo=FALSE}
table <-  MIR_data$sample_data %>%
            group_by(PROT, STRAT) %>%
            summarise(n = length(unique(PRIMARY_SAMPLE_UNIT))) %>%
            mutate(description = case_when(
              STRAT == "FK01" ~ "inshore reefs, all depths",
              STRAT == "FK02" ~ "mid-channel patch reefs, all depths",
              STRAT == "FK03" ~ "offshore patch, all depths",
              STRAT == "FK04" ~ "forereef, low rugosity, <12m",
              STRAT == "FK05" ~ "forereef, high rugosity, <12m"
            )) %>%
            mutate(PROT = case_when(
              PROT == 0 ~ "Outside",
              PROT == 1 ~ "Inside"
            )) %>% 
            select(PROT, STRAT, description, n) %>%
            ungroup()

knitr::kable(table, caption = "Table 1. Number of sites sampled.", format = "latex")

```

## Fish Species

A selection of fish species were chosen to represent different trophic levels and functional roles. 

```{r echo=FALSE}
spp_list <- tribble(
  ~SPECIES_CD, ~CommonName, ~SciName,
  "HAE FLAV", "French grunt", "Haemulon flavolineatum",
  "SPA VIRI", "Stoplight parrotfish", "Sparisoma viride",
  "SCA GUAC", "Rainbow parrotfish", "Scarus guacamaia", 
  "STE PLAN", "3-spot damselfish", "Stegastes planifrons",
  "CAL CALA", "Porgy", "Calamus calamus",
  "CAL NODO", "Porgy", "Calamus nodosus"
) %>%
as.data.frame()

knitr::kable(spp_list, caption = "Table 2. Fish species. For analysis, both porgy species were combined.", format = "latex")
```


## Density
Density is represented as the number of individuals per 177 m^2.
```{r}
MIR_domain_dens_by_year(MIR_data, spp_list)
```

## Occurrence
Survey occurrence within MIR sites and outside. 
```{r}
MIR_domain_occ_by_year(MIR_data, spp_list)
```

## Length Frequency {.tabset}
Relative length frequency of species within MIR sites and outside. 

### French Grunt
```{r, fig.show="hold", out.width="50%"} 
MIR_LF(df = MIR_data, spp = "hae flav", bin_size = 5, yrs = 2022, spp_name = "French grunt")
MIR_LF(df = MIR_data, spp = "hae flav", bin_size = 5, yrs = 2024, spp_name = "French grunt")
```

### Stoplight Parrotfish
```{r, fig.show="hold", out.width="50%"} 
MIR_LF(df = MIR_data, spp = "spa viri", bin_size = 5, yrs = 2022, spp_name = "Stoplight parrotfish")
MIR_LF(df = MIR_data, spp = "spa viri", bin_size = 5, yrs = 2024, spp_name = "Stoplight parrotfish")
```

### Rainbow Parrotfish
```{r, fig.show="hold", out.width="50%"} 
MIR_LF(df = MIR_data, spp = "sca guac", bin_size = 5, yrs = 2022, spp_name = "Rainbow parrotfish")
MIR_LF(df = MIR_data, spp = "sca guac", bin_size = 5, yrs = 2024, spp_name = "Rainbow parrotfish")
```

### 3-Spot Damselfish
```{r, fig.show="hold", out.width="50%"} 
MIR_LF(df = MIR_data, spp = "ste plan", bin_size = 2, yrs = 2022, spp_name = "3-spot damselfish")
MIR_LF(df = MIR_data, spp = "ste plan", bin_size = 2, yrs = 2024, spp_name = "3-spot damselfish")
```

### Porgy
```{r, fig.show="hold", out.width="50%"} 
MIR_data_copy <- MIR_data
MIR_data_copy$sample_data <- MIR_data_copy$sample_data %>%
  mutate(SPECIES_CD = if_else(SPECIES_CD == "CAL CALA", "CAL NODO", SPECIES_CD))
#Merged CAL CALA and CAL NODO to graph both porgy species together
MIR_LF(df = MIR_data_copy, spp = "CAL NODO", bin_size = 2, yrs = 2022, spp_name = "Porgy")
MIR_LF(df = MIR_data_copy, spp = "CAL NODO", bin_size = 2, yrs = 2024, spp_name = "Porgy")
```
